Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-06 docs/ms.tex
Update ms.tex

\begin{equation}
p(\epsilon_{\ell}|\vec{g},\alpha)=p(\epsilon_{0}(\vec{g})|\alpha)*|\frac{\partial\epsilon_{0}}{\,}{\partial\epsilon_{\ell}}|
\end{equation}

@@

If there is measurement error on $\epsilon_{ob}$,we will have 
\begin{equation}
p(\epsilon_{ob}|\vec{g},\alpha)=\int f(\epsilon_{ob}|\epsilon_{\ell})\, p(\epsilon_{\ell}|\vec{g},\alpha)
\end{equation}
Here the prior distribtuion we use for $\vec{g}$ is a 2D flat distribution
in the region $|g|<1$.Therefore $p(\vec{g)}=\begin{cases}
1 & |\vec{g}|<1\\
0 & |\vec{g}|>1
\end{cases}$

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  SECTION X: DISCUSSION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\label{sec:discuss}

>>>>

\begin{equation}
p(\epsilon_{\ell}|\vec{g},\alpha)=p(\epsilon_{0}(\vec{g})|\alpha)\,|\frac{\partial\epsilon_{0}}{\partial\epsilon_{\ell}}|
\end{equation}

@@

If there is measurement error on $\epsilon_{ob}$,we will have 
\begin{equation}
p(\epsilon_{ob}|\vec{g},\alpha)=\int f(\epsilon_{ob}|\epsilon_{\ell})\, p(\epsilon_{\ell}|\vec{g},\alpha)
\end{equation}
Here the prior distribtuion we use for $\vec{g}$ is a 2D flat distribution
in the region $|\vec{g}|<1$.Therefore $p(\vec{g)}=1$ if $|\vec{g}|<1$
and $p(\vec{g})=0$ if $|\vec{g}|>1$.

@@
